Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-26 paper/presentation/DASFAA_presentation.tex
add example for page 6
add "hood" picture
fix page 18

@@

\begin{frame}
\frametitle{How about existing methods? (2/2)}
Event detection methods \textit{by leveraging extra information}
\begin{enumerate}
	\item typical one: Twevent[Li, CIKM 2012]
	\begin{itemize}
		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
		\item detects the bursty segments and cluster these segments into candidate events
		\item still has to trade off between precision and recall
	\end{itemize}
\end{enumerate}
\end{frame}

@@

\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=0.5\columnwidth, left]{Fort_Hood.pdf}
\end{figure}
\end{frame}

@@

%------------------------------
%page 12
\begin{frame}
\frametitle{Experimental Results}
Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015].

@@

\begin{frame}
\frametitle{Experimental Results}	
Evaluation on Categroy-Level Topics in Knowledge Base.
On more topics, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]. 
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/NPMI.pdf}
        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
        \label{fig:NPMI}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}	
\begin{itemize}
	\item Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized microblog stream. 
	\item We propose \textsc{TransDetector} method, and
	\begin{itemize}
		\item use category-level topic in knowledge base as the prior knowledge,
		\item transfer abundant knowledge from knowledge base into microblog stream
		\item enrich the semantics of microblogs and further enhances the accuracy of microblogs event detection
	\end{itemize}
\end{itemize}
\end{frame}

>>>>

\usepackage{subfigure}

@@

\begin{frame}
\frametitle{How about existing methods? (2/2)}
Event detection methods \textit{by leveraging extra information}
\begin{enumerate}
	\item typical one: Twevent[Li, CIKM 2012]
	\begin{itemize}
		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
		\item detects the bursty segments and cluster these segments into candidate events
		\item still has to trade off between precision and recall
		\begin{itemize}
			\item e.g., the bursty segment in the not-so-popular event ``\textit{first artificial organ transplant}" is missed
		\end{itemize}
	\end{itemize}
\end{enumerate}
\end{frame}

@@

\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
	\centering
        \subfigure[]{
                \includegraphics[height=2.12cm]{Hood(headgear)-Wikipedia.pdf}
        }
        \subfigure[]{
                \includegraphics[height=2.12cm]{Fort_Hood.pdf}
        }
\end{figure}

@@

%------------------------------
%page 12
\begin{frame}
\frametitle{Experimental Results}
Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.

@@

\begin{frame}
\frametitle{Experimental Results}	
Evaluation on Categroy-Level Topics in Knowledge Base.
On more topics, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Roder, WSDM 2015]. 
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/NPMI.pdf}
        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
        \label{fig:NPMI}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}	
\begin{itemize}
	\item Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized microblog stream. 
	\item We propose \textsc{TransDetector} method, and
	\begin{itemize}
		\item use category-level topic in knowledge base as the prior knowledge,
		\item transfer abundant knowledge from knowledge base into microblog stream
		\item enrich the semantics of microblogs and further enhances the accuracy of microblogs event detection
	\end{itemize}

\end{itemize}
\end{frame}
